Catching fire: Undefined behaviour for equational reasoning of lazy languages with strictness annotations

### 2021-01-21 paper/paper.tex
add example of computing sum of first n numbers

>>>>

\begin{lstlisting}[language=llvm, caption="example of laziness with tensor computations"]
module {
// sum up all values in the buffer
func @sum(%buffert: !lz.thunk<memref<?xi64>>) -> i64 {
  %buffer = lz.force(%buffert) :  memref<?xi64>
  %c0 = constant 0 : index
  %N = dim %buffer, %c0 : memref<?xi64>
  %sum_0 = constant 0 : i64
  %sum = affine.for %i = 0 to %N step 1
  iter_args(%sum_iter = %sum_0) -> (i64) {
    %t = affine.load %buffer[%i] : memref<?xi64>
    %sum_next = std.addi %sum_iter, %t : i64
    affine.yield %sum_next : i64
  }
  return %sum : i64
}

// create a sequence [0..upper_bound)
func @seq(%upper_bound: i64) ->  memref<?xi64> {
  %upper_bound_ix = std.index_cast %upper_bound : i64 to index
  %buf = alloc(%upper_bound_ix) : memref<?xi64>
  affine.for %i = 0 to %upper_bound_ix step 1 {
    %ival = std.index_cast %i : index to i64
    affine.store %ival, %buf[%i] : memref<?xi64>
  }
  return %buf : memref<?xi64>
}

func private @printInt(%i: i64)

// computes sum of numbers upto 1023?
func @main ()  -> i64 {
  %seqf = constant @seq : (i64) ->  memref<?xi64>
  %size = std.constant 1024 : i64
  %seqt = lz.ap(%seqf: (i64) -> memref<?xi64>, %size)

  %sumf = constant @sum : (!lz.thunk<memref<?xi64>>) -> i64
  %outt = lz.ap(%sumf : (!lz.thunk<memref<?xi64>>) -> i64, %seqt)
  %outv = lz.force(%outt): i64
  call @printInt(%outv) : (i64) -> ()
  %zero = constant 0 : i64
  return %zero : i64
}
}
\end{lstlisting}

\sid{MLIR can work harder, but it does not. By the time we get to LLVM, we have a closed form}
\begin{lstlisting}[language=llvm, caption="final program after eliminating laziness and loop fusion"]
func @main() -> i64 {
  %c0_i64 = constant 0 : i64
  %0 = alloc() : memref<1xi64>
  %1 = affine.for %arg0 = 0 to 1024 iter_args(%arg1 = %c0_i64) -> (i64) {
    %2 = index_cast %arg0 : index to i64
    affine.store %2, %0[0] : memref<1xi64>
    %3 = affine.load %0[0] : memref<1xi64>
    %4 = addi %arg1, %3 : i64
    affine.yield %4 : i64
  }
  call @printInt(%1) : (i64) -> ()
  return %c0_i64 : i64
}
\end{lstlisting}

\begin{lstlisting}[language=llvm, caption="final LLVM program after lowering"]
define i64 @main() local_unnamed_addr !dbg !35 {
  tail call void @printInt(i64 523776), !dbg !36
  ret i64 0, !dbg !38
}
\end{lstlisting}
